Estimating the association between Facebook adoption and well-being in 72 countries

### 2022-09-16 ms.Rmd
Edit title

---
title: Estimating the association between Facebook adoption and well-being

@@

We found that, overall, Facebook adoption positively predicted well-being. This association held when comparing countries to other countries and to themselves over time. While these descriptive results do not speak to causal effects, they align with other recent findings suggesting that technology has not become increasingly harmful over time [@vuorreThereNoEvidence2021], and that the increased adoption of Internet technologies is not, overall, associated with widespread psychological harms [@vuorreGlobalWellbeingMental2022]. That said, these conclusions are qualified because our focus on daily active users could miss those who use Facebook less regularly. To test this possibility, we also conducted our analyses using monthly active Facebook users (MAU) as the predictor. Those results were substantively the same (see online supplement).

@@

Both datasets (Facebook and Gallup) are proprietary and we therefore could not share them with this manuscript. Our analytic code, along with synthetic datasets, is available at (LINK). Researchers can contact Facebook (ccobb@fb.com) to reproduce our analyses with the actual Facebook adoption dataset. The Gallup data are available online to subscribing institutions.

>>>>

---
title: Estimating the association between Facebook adoption and well-being in 72 countries

@@

We found that, overall, Facebook adoption positively predicted well-being. This association held when comparing countries to other countries and to themselves over time. While these descriptive results do not speak to causal effects, they align with other recent findings suggesting that technology has not become increasingly harmful over time [@vuorreThereNoEvidence2021], and that the increased adoption of Internet technologies is not, overall, associated with widespread psychological harms [@vuorreGlobalWellbeingMental2022]. That said, these conclusions are qualified because our focus on daily active users could miss those who use Facebook less regularly. To test this possibility, we also conducted our analyses using monthly active Facebook users (MAU) as the predictor. Those results were substantively the same (see online analysis supplement; <https://doi.org/10.5281/zenodo.7086277>).

@@

Both datasets (Facebook and Gallup) are proprietary and we therefore could not share them with this manuscript. Our analytic code, along with synthetic datasets and an online analysis supplement, is available at <https://doi.org/10.5281/zenodo.7086277>. Researchers can contact Facebook (ccobb@fb.com) to reproduce our analyses with the actual Facebook adoption dataset. The Gallup data are available online to subscribing institutions.
